
\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel size (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, it is not true that the value of the density is 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 

It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
to solutions of the Neumann problem in order to obtain full machine precision ($\sim 1.11 \times 10^{-16}$) for the solution anywhere in the volume sufficiently far from the corner.
However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed via dense linear solves.

The potential at target locations which are more than 1 panel length away is the inner product of the 
density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations for a scattering problem whose right hand side is given by a collection of three interior charges
\begin{equation}
u(\bx) = \sum_{j=1}^{3} \log |\bx - \bx_{j}| \, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:analytictest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary. 

Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
-0.823641009939200 & -0.139714174784448 \\
 -0.139714174784448 &  -1.1421444446470226
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
2.3 \times 10^{-15} & 7.9 \times 10^{-16} \\
1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
\end{bmatrix}
\end{equation}

In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}. Furthermore, to highlight the need for special purpose discretizations in the vicinity of corners in the adjoint method, we also compare the solution computed using a graded mesh in the vicinity of corners, where the smallest panel is identical
to the one after resolves. So for 20 iterations, the smallest panel is $2^{-20}$ times the original panel, for $40$ iterations,
the smallest panel is $2^{-40}$ times the original panel and so on.

After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\subsection{Performance}
In this section, we demonstrate the performance of the solver of two large domains. We solve scattering problems in the
exterior of a magnetron like region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that 